---
title: "Project"
author: "Logan Morrill"
date: "11/10/2021"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---

```{r include = FALSE}
#Packages
library(tidyverse)
library(dygraphs)
library(lubridate)
library(tidyquant)
library(timetk)
```

```{r Stock Comparison}
#Stock 1 Year Comparison Function
stonk_calculator <- function(tickers) {
  stonks <- tq_get(tickers, get = "stock.prices", from = today() - years(1), to = today())
  stonks_chart <- stonks %>%
    select(symbol, date, adjusted) %>%
    pivot_wider(names_from = symbol, values_from = adjusted) %>%
    tk_xts(date_var = date)
  dygraph(stonks_chart)
}

```
### Try to Find High Correlated Stock Pair for Pair Trading
```{r GM and F Pair}
#Compare Stock Returns for General Motors (GM) and Ford (F) to find a pair
GM_F <- c('GM','F')

stonk_calculator(GM_F)
```

```{r GLD and SLV Pair}
#Compare ETF Returns for Gold (GLD) and Silver (SLV) to find a pair
GLD_SLV <- c('GLD','SLV')

stonk_calculator(GLD_SLV)
```

```{r SPY and QQQ Pair}
#Compare ETF Returns for S & P (SPY) and Nasdaq (QQQ) to find a pair
SPY_QQQ <- c('SPY','QQQ')

stonk_calculator(SPY_QQQ)
```

  Looking at the charts directly it is hard to tell if any three pair are highly correlated. There might be some correlation between SPY and QQQ but the other 2 pairs seem to not be correlated. 
  I will need to use standard deviation to see if the pairs revert back to their means. This will tell me if the pair is truly correlated and I can trade the pair.

 Timeline: 
I would like to have my first draft done by November 19.
I want my second draft done by November 22.
I want the final draft done by November 29. 
I could then present to 2-3 friends on the 2nd. 
I would like to present on Tuesday, December 7th. 