---
title: "Task 10"
author: "Logan Morrill"
date: "9/28/2021"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---

### Load packages
```{r include = FALSE}
#Packages
library(tidyverse)
```
### Load data
```{r}
?ToothGrowth
head(ToothGrowth)
str(ToothGrowth)
```

```{r Supplement type}
ggplot(ToothGrowth, aes(supp, len)) +
  geom_boxplot(aes(fill = supp)) +
  scale_fill_manual(values = c('orange','yellow')) +
  scale_y_continuous(limits = c(0,40), breaks = seq(0,40,4)) +
  scale_x_discrete(labels = c('Orange Juice', 'Ascorbic Acid')) +
  labs(x = 'Vitamin C Delivery', y = 'Tooth length', title = 'Supplement Delivery effect on Tooth Length',
       subtitle = 'Does the mode of delivery of vitamin C effect the tooth length of guinea pigs?') +
  theme_bw() +
  theme(legend.position = 'none')
```
This graph shows the result of the vitamin C delivery method had on the tooth length. I choose a box plot because it shows the range, the median, and the quartiles of the data. Ascorbic Acid has a bigger range of tooth length but Orange Juice has a higher median.


```{r Vitamin C dose}
ggplot(ToothGrowth, aes(factor(dose), len)) +
  geom_col(aes(fill = dose)) +
  scale_x_discrete(labels = c('0.5', '1','2' )) +
  labs(x = 'Vitamin C dose (mg/day)', y = 'Tooth length', title = 'Vitamin C effect on Tooth Length',
       subtitle = 'Does different amounts of vitamin C effect the tooth length of guinea pigs?') +
  theme_bw() +
  theme(legend.position = 'none')
```

```{r Weight vs quarter mile}
?mtcars
head(mtcars)
ggplot(mtcars, aes(x = qsec, y = wt)) +
  geom_point(aes(color = factor(cyl))) +
  geom_smooth(method = 'lm', color = 'black') +
  labs(x = 'Quarter Mile Time (sec)', y = 'Weight (1000 lbs)', title = 'Car Weight on quarter mile time',
       subtitle = 'Does the weight have an effect on the Quarter Mile Time?') +
  scale_color_discrete(name = 'Engine Cylinders') +
  theme_bw()
```
I choose to do a linear regression to show the relationship between the weight and quarter mile time. It seems there may be a slight negative correlation but the confidence intervals are too wide to tell. I also grouped the data points by engine cylinders. The more cylinders in the engine means the more weight, but a higher quarter mile time.
```{r hp vs mpg}
ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point(aes(color = factor(cyl))) +
  geom_smooth(method = 'lm', color = 'black') +
  labs(x = 'Horsepower (hp)', y = 'Miles per Gallon (mpg)', title = 'Horsepower vs miles per gallon',
       subtitle = 'Does the horsepower effect the miles per gallon?') +
  scale_color_discrete(name = 'Engine Cylinders') +
  theme_bw()
```
I choose to do a linear regression to show the relationship between the horsepower and the miles per gallon. There is a significant negative correlation. I also grouped the data points by engine cylinders. The more cylinders in the engine increases the horsepower, but decreases the miles per gallon.
