---
title: "Counting Names in Scripture"
author: "Logan Morrill"
date: "10/20/2021"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---

```{r include = FALSE}
#Packages
library(tidyverse)
library(downloader)
library(stringi)
```

```{r include = FALSE}
#Load Data
csv_data <- tempfile()
#Bible Data
download("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/bible.csv", 
csv_data, mode = "wb")
bible_Data <- read_csv(csv_data)
#Name Data
download("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/Names.csv", 
csv_data, mode = "wb")
name_Data <- read_csv(csv_data)
```

```{r include = FALSE}
#Old testament Verses
old_testament_scripts <- bible_Data %>%
  filter(volume_long_title == 'The Old Testament') %>%
  select(scripture_text) %>%
  str_c()
#New testament Verses
new_testament_scripts <- bible_Data %>%
  filter(volume_long_title == 'The New Testament') %>%
  select(scripture_text) %>%
  str_c()
savior_names <- name_Data %>%
  select(name)
```

```{r Each Instance of Savior Name}
#Function to find number of savior references
savior_references <- function(df) {
  count <- vector("integer", ncol(savior_names))
  for (name in savior_names) {
      count <- count + str_length(str_extract_all(df,name))
  }
  sum(count)
}
#Old Testament Savior References
savior_references(old_testament_scripts)
#33,187
#New Testament Savior References
savior_references(new_testament_scripts)
#44,280
```

```{r Words between Function}
#Function to find words between instances
words_between <- function(df, test) {
  for (names in savior_names$name) {
    name_replace <- str_replace_all(df, names, '1234')
  }
  word_split <- str_split(name_replace, '1234')
  word_split_n <- str_remove_all(word_split, '\n')
  if (test == 'mean') {
    stri_stats_latex(unlist(word_split_n))[[4]]/ length(unlist(word_split))
  } else {
    stri_stats_latex(unlist(word_split_n))[[4]]
  }
}
```

```{r Words between instances}
#Old testament words between instances
words_between(old_testament_scripts, 'between')
#611,503

#New testament words between instances
words_between(new_testament_scripts, 'between')
#180,662

#Average Old testament words between instances
words_between(old_testament_scripts, 'mean')
#3,135.913

#Average New testament words between instances
words_between(new_testament_scripts, 'mean')
#12,044.13
```
  It looks like the New Testament has more references to the Savior name the Old Testament, 33,187 vs. 44,280. It also looks like the Old Testament has more words between the Savior names than the New Testament, 661,503 words with the average words between names being 3135.913. The New Testament has less words, 180,662 however it has a higher average between names of 12044.13.
  All three of these conclusion indicate the New Testament could be longer than the Old Testament. 


