---
title: "Task 4"
author: "Logan Morrill"
date: "9/7/2021"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---


```{r include = FALSE}
# Load Packages
library(tidyverse)
library(downloader)
library(readxl)
```
##### Load Data
```{r Load Data}
SoloData <- tibble(read_csv("solo-artist-followers.csv"))
head(SoloData)
BillboardData <- tibble(read_csv("billboard-hits.csv"))
str(BillboardData)

#Change peak_date to date
BillboardData <- read_csv(
  ("billboard-hits.csv"),
  col_types = cols(
    peak_date = col_date()
  )
)
str(BillboardData)
```

All data types seem to be imported correctly, except the peak_date for billboard data.
Peak_date had to be converted to data type date.

#### Get hits data
```{r Filter billboard data}
atleast_six_hits <- BillboardData %>%
  group_by(name) %>%
  filter(n() > 6 & band != "")

view(atleast_six_hits)
str(atleast_six_hits)
```

```{r Get Band Hits}
band_hits <- BillboardData %>% 
  group_by(band) %>%
  filter(name %in% atleast_six_hits$band)
#Switch band and name column data
band_hits <- rename(band_hits, band = name, name = band)
head(band_hits)
```
#### Graph
```{r Graphing}
ggplot(data = atleast_six_hits, aes(x = peak_date, y = peak_rank, color = name, group = name)) +
  geom_point() +
  geom_line() +
  geom_point(data = band_hits, color = 'black') +
  geom_line(data = band_hits, color = 'black',linetype = 'dotted') +
  facet_wrap(~band, scales = "free") +
  theme_bw()
```
It seems that majority of the top 100 hits for the bands are a result of having a good singer.
However, the Jonas Brothers, One Direction, and New Edition have had several top 100 hits regardless of the singer.
Beyonce seems to be the cause of majority of Destiny's Child top 100 hits.

### Additional data
```{r Microsoft Data}

microsftData <- tibble(read.csv("MSFT.csv"))
#Change data to data type date
microsftData <- read_csv(
  ("MSFT.csv"),
  col_types = cols(
    Time = col_date()
  )
)
str(microsftData)
```
https://finance.yahoo.com/quote/MSFT/history?p=MSFT
Microsoft data for 1 year for daily candles
```{r Shark Sighting Data}
june_2021_employment_Data <- tibble(read_csv("business-employment-data-june-2021-quarter.csv"))
str(june_2021_employment_Data)
```
https://www.stats.govt.nz/large-datasets/csv-files-for-download/
Employment Data for quarter in June 2021
```{r Cattle Price Data}
cattle_priceData <- tibble(read_csv("cattle-futures.csv"))
#Change data to data type date
cattle_priceData <- read_csv(
  ("cattle-futures.csv"),
  col_types = cols(
    date = col_date("%m/%d/%Y")
  )
)
str(cattle_priceData)
```
https://www.macrotrends.net/futures/cattle
Cattle Futures prices by year from 1964 to 2021