---
title: "Task 4"
author: "Logan Morrill"
date: "9/7/2021"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---

##### Load Packages
```{r Packages}
library(tidyverse)
library(dplyr)
library(downloader)
library(readxl)
```
##### Load Data
```{r Load Data}
SoloData <- tibble(read.csv("solo-artist-followers.csv"))
head(SoloData)
BillboardData <- tibble(read.csv("billboard-hits.csv"))
str(BillboardData)

#Change peak_date to date
BillboardData <- read_csv(
  ("billboard-hits.csv"),
  col_types = cols(
    peak_date = col_date()
  )
)
str(BillboardData)
```

All data types seem to be imported correctly, except the peak_date for billboard data.
Peak_date had to be converted to data type date.

#### Get hits data
```{r Filter billboard data}
atleast_six_hits <- BillboardData %>%
  group_by(name) %>%
  filter(n() > 6 & band != "")

view(atleast_six_hits)
str(atleast_six_hits)
```

```{r Get Band Hits}
band_hits <- BillboardData %>% 
  group_by(band) %>%
  filter(name %in% atleast_six_hits$band)
#Switch band and name column data
band_hits <- rename(band_hits, band = name, name = band)
view(band_hits)
```
#### Graph
```{r Graphing}
ggplot(data = atleast_six_hits, aes(x = peak_date, y = peak_rank, color = name, group = name)) +
  geom_point() +
  geom_line() +
  geom_point(data = band_hits, color = 'black') +
  geom_line(data = band_hits, color = 'black',linetype = 'dotted') +
  facet_wrap(~band, scales = "free") +
  theme_bw()
```
It seems that majority of the top 100 hits for the bands are a result of having a good singer.
However, the Jonas Brothers, One Direction, and New Edition have had several top 100 hits regardless of the singer.
Beyonce seems to be the cause of majority of Destiny's Child top 100 hits.

### Additional data
```{r Microsoft Data}
#https://finance.yahoo.com/quote/MSFT/history?p=MSFT
#Microsoft data for 1 year for daily candles
microsftData <- tibble(read.csv("MSFT.csv"))
#Change data to data type date
microsftData <- read_csv(
  ("MSFT.csv"),
  col_types = cols(
    Date = col_date()
  )
)
str(microsftData)
```

```{r Shark Sighting Data}
#https://www.google.com/earth/outreach/learn/visualize-your-data-on-a-custom-map-using-google-my-maps/
#Great white shark sightings along the False Bay coastline in South Africa from September 8, 2012 to February 22, 2013
sharkData <- tibble(read.csv("sharksightings.csv"))
```