---
title: "Case Study 4"
author: "Logan Morrill"
date: "9/15/2021"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---


```{r Packages, include = FALSE}
# Load Packages
library(nycflights13)
library(tidyverse)
```
##### Load Data
```{r Load Data}
flightData <- tibble(flights)
head(flightData)
str(flightData)

```
### Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?

```{r Best departure airport}
?flights
head(airlines)

best_delta_arrival_flights <- flightData %>%
  select(carrier, year:day, arr_delay, origin) %>%
  group_by(origin) %>%
  filter(carrier == "DL") %>%
  arrange(arr_delay)
head(best_delta_arrival_flights)

#Find out the name of the best airport for arrival
?airports
airports %>%
  select(faa, name) %>%
  filter(faa == "JFK")
```
John F Kennedy International is the best airport to depart from to minimize arrival delay on Delta Airline flights.

### Which destination airport is the worst airport for arrival time?
```{r Worst airport for arrival}
worst_airport_delayed_arrival <- flightData %>%
  group_by(origin) %>%
  summarise(
    avg_arrival_delay = mean(arr_delay, na.rm = TRUE))
head(worst_airport_delayed_arrival)

#Find out the name of the worst airport for arrival
?airports
airports %>%
  select(faa, name) %>%
  filter(faa == "EWR")
```
Newark Liberty International it the worst airport for arrival time with an average delay of 9.1 minutes.
### Graphs
```{r Worst airport graph }
ggplot(data = flightData, aes(x = origin, y = arr_delay)) +
  geom_point(aes(color = origin)) +
  geom_point(data = worst_airport_delayed_arrival, aes(y = avg_arrival_delay, color = 'red', size = 1)) +
  annotate("text", x = c(1.1,2.1,3.1), y = 30, label = c("9.107", "5.551", "5.783")) +
  xlab("Airport") + ylab("Arrival Delay (minutes)") + ggtitle("Airport Arrival Delays") +
  theme(axis.text.x = element_text(color = "grey20", size = 13),
        axis.text.y = element_text(color = "grey20", size = 13),  
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        plot.title = element_text(size = 22),
        legend.position = 'none')
```
The graph confirms that EWR is th worst airport for arrival with an average delay that is almost twice as much as the other 2 airports. The delay of almost double could suggest that EWR has longer flights.

```{r}
ggplot(data = flightData, aes(x = dep_delay, y = arr_delay)) +
  geom_point(aes(color = origin)) +
  geom_smooth(color = 'black') +
  xlab("Departure Delay (minutes)") + ylab("Arrival Delay (minutes)") + ggtitle("Airport Arrival Delays") +
  labs(color = 'Departure Airport')
```
The graph shows a significant correlation for departure delay and arrival delay, which is not surprising. If a flight departs late, it will arrive late. It also suggest distance is not a factor in delay because the plane departs late. This means the delay will be more of an internal problem.


```{r Best flight graph }
ggplot(data = flightData, aes(x = carrier, y = arr_delay)) +
  geom_point(aes(color = origin)) +
  xlab("Carriers") + ylab("Arrival Delay (minutes)") + ggtitle("Airport Arrival Delays") +
  labs(color = 'Departure Airport')
```
The graph confirms that JFK has the best chances to minimize the chances of a late arrival when flying Delta Airlines. The graph also shows that some carriers exclusively fly out of certain airports. It is hard to tell by the graph, but the data might suggest that flying with an exclusive carrier will minimize the chance of a late arrival.